How to select predictive models for decision-making or causal inference?

### 2023-12-16 how_to_select_causal_models.tex
cosmetics
"Double spacing"
(or actually, something that looks a bit like it, but isn't, because
double spacing is too ugly)
iter

@@

\onecolumn
\maketitle
\begin{abstract}\noindent
    \textbf{Objective:}
    To evaluate which procedure selects the predictive model most
    trustworthy to reason on the effect of an intervention and support
    decision making.\\
    %As predictive models --\eg from machine learning-- give likely
    %outcomes, they may be used to, a
    %causal-inference task. The increasing complexity of health data has opened
    %the door to a plethora of models, but also the Pandora box of model
    %selection: which of these models yield the most valid causal estimates? 
    \textbf{Methods:}
    We study such a variety of model selection procedures in practical settings:
    finite samples settings and without well-specification assumption.
    Elaborate risks build proxies of the causal error using ``nuisance''
    re-weighting to compute it on the observed data. We evaluate whether
    empirically estimated nuisances, which are necessarily noisy,
    add noise to model selection. Drawing from an extensive empirical
    study based on a simulation and three healthcare datasets
    based on real covariates, we compare different metrics for causal model
    selection.\\
    \textbf{Results:} Among all metrics the classical mean squared error (ie.
    factual $\mu\mathrm{-risk}$) is worse and re-weighting it with propensity score
    ($\mu\mathrm{-risk}_{IPW}$) does not bring much improvements. The
    $R\text{-risk}$, which includes a model of mean outcome and propensity
    scores, leads to the best performances.\\
    \textbf{Conclusions:} We outline that evaluating models for causal
    reasoning requires different procedures than standard predictive
    settings: using the so-called $R\text{-risk}$ with nuisance
    corrections computed with flexible estimators.
\end{abstract}
\keywords{Model Selection, Treatment Effect, G-formula, Observational Study, Machine Learning, }
\clearpage

% XXX: for submission
%\twocolumn
\section{Introduction}\label{sec:intro}

>>>>

\usepackage[%
    font={footnotesize,sf},
    labelfont=bf,
    format=hang,    
    format=plain,
    margin=0pt,
]{caption}

% XXX: for submission
\usepackage{setspace}

@@

\onecolumn
\maketitle
\begin{abstract}\noindent
    \textbf{Objective:}
    We investigate which procedure selects the predictive model most
    trustworthy to reason on the effect of an intervention and support
    decision making.\\
    %As predictive models --\eg from machine learning-- give likely
    %outcomes, they may be used to, a
    %causal-inference task. The increasing complexity of health data has opened
    %the door to a plethora of models, but also the Pandora box of model
    %selection: which of these models yield the most valid causal estimates? 
    \textbf{Methods:}
    We study such a variety of model selection procedures in practical settings:
    finite samples settings and without theoretical assumption of 
    \emph{well-specified} models. Beyond standard cross-validation or
    internal validation procedures, we also study elaborate causal risks.
    These build proxies of the causal error using ``nuisance''
    re-weighting to compute it on the observed data. We evaluate whether
    empirically estimated nuisances, which are necessarily noisy,
    add noise to model selection. We compare different metrics for
    causal model selection in an extensive empirical
    study based on a simulation and three healthcare datasets
    based on real covariates. \\
    \textbf{Results:} Among all metrics the classical mean squared error (ie.
    factual $\mu\mathrm{-risk}$) is worse and re-weighting it with propensity score
    ($\mu\mathrm{-risk}_{IPW}$) does not bring much improvements. The
    $R\text{-risk}$, which includes a model of mean outcome and propensity
    scores, leads to the best performances.\\
    \textbf{Conclusions:} We outline that evaluating models for causal
    reasoning requires different procedures than standard predictive
    settings: using the so-called $R\text{-risk}$ with nuisance
    corrections computed with flexible estimators.
\end{abstract}
\keywords{Model Selection, Treatment Effect, G-formula, Observational Study, Machine Learning, }
\clearpage

% XXX: for submission
%\twocolumn
% XXX: for submission
\setstretch{1.1}
\section{Introduction}\label{sec:intro}
